\section{a prayer for singers}

\begin{center}
   {\textit{\small Adapted from Abbess Thaisa's prayers}}
\end{center}


\epigraph{O come, let us worship and fall down before Him, and let us weep before the Lord Who made us.}{\textit{Ps. 94:6}}

O Lord Jesus Christ, Thou hast said, 'Without me ye can do nothing.' I therefore beseech Thee, may Thy grace be upon me, bringing attentiveness to my heart and sobriety into my mind. May my mouth, which Thou hast fashioned, become the mouth of the Church. May I sing and chant not for myself only but for all present in the Church. May I sing with understanding, taking heed that I am present before Thy dread Throne, coming before Thine invisible face, O Thou King of Glory, presenting my feeble and insignificant voice to participate with the innumerable angels and all the Heavenly Hosts in their ceaseless and ineffable doxology to Thee. Enlighten my heart that I may begin to fathom the importance of the work I perform by Thy mercy. Grant, O Lord, that I may sing not only with my lips but with the heart; singing with all my mind, soul, will, desire, and my whole being. May every part of me become luminous with Thy Divine light as I participate in Thy Grace and glorify Thee. O Lord, may I strive with all my strength to concentrate attentively on the words I pronounce. Grant that they would come from the depth of my soul. May the vivifying grace of the Holy Spirit that is vested in them pour into the hearts of those who hear them, and may they who hear be raised from earth to heaven, becoming enlightened, strengthened and sanctified by Thy might. O Sun of Righteousness, shine on us and in our hearts that we, in humility of mind and holiness of heart, might praise Thee with fitting hymns from our lips of clay. May our prayers become a sweet spiritual fragrance that rises before Thee for all mankind, filled with hope and love toward Thee. Grant that we who praise Thee would be united by Thy Holy Spirit in the bond of love, that with one mouth and one heart we might praise, bless, glorify, and worship Thee, the Light above all Lights, the True Life, and the Salvation that abideth unto the ages of ages. Amen.


Glory and Praise unto Thee, O Lord, Glory to Thee!

