\section[Section Title\\Section Subtitle]{great doxology \\{\normalfont \normalsize \textit{for Romanian Liturgy}}}

\begin{verse}
    Glory to God in the highest, \\
    and on earth peace, good will among men. \\
    We praise Thee, we bless Thee, \\
    we worship Thee, we glorify Thee, \\
    we give thanks to Thee for Thy great glory. \\
    O Lord, heavenly King, God the Father Almighty; \\
    O Lord, the Only-Begotten Son, Jesus Christ; and O Holy Spirit. \\
    O Lord God, Lamb of God, Son of the Father, \\
    that takest away the sin of the world, have mercy on us; \\
    Thou that takest away the sins of the world, receive our prayer; \\
    Thou that sittest at the right hand of the Father, have mercy on us. \\
    For Thou only art holy, \\
    Thou only art the Lord, O Jesus Christ, to the glory of God the Father. Amen. \\!

    Every day will I bless Thee and I will praise Thy name forever, yea forever and ever. \\
    Vouchsafe, O Lord, to keep us this day without sin. \\
    Blessed art Thou, O Lord, the God of our fathers, \\
    and praised and glorified is Thy name unto the ages. Amen. \\
    Let Thy mercy, O Lord, be upon us according as we have hoped in Thee. \\
    Blessed art Thou, O Lord, teach me Thy statutes. \\
    Blessed art Thou, O Lord, teach me Thy statutes. \\
    Blessed art Thou, O Lord, teach me Thy statutes. \\
    Lord, Thou hast been our refuge in generation and generation. \\
    I said: O Lord, have mercy on me, heal my soul, for I have sinned against Thee. \\
    O Lord, unto Thee have I fled for refuge, teach me to do Thy will, for Thou art my God; \\
    For in Thee is the fountain of life, in Thy light shall we see light. \\
    O continue Thy mercy unto them that know Thee. \\!

    Holy God, Holy Mighty, Holy Immortal, have mercy on us. \\
    Holy God, Holy Mighty, Holy Immortal, have mercy on us. \\
    Holy God, Holy Mighty, Holy Immortal, have mercy on us. \\!

    Glory to the Father, and to the Son, and to the Holy Spirit, both now and ever, and unto the ages of ages. Amen. \\
    Holy Immortal, have mercy on us. \\!

    Holy God, Holy Mighty, Holy Immortal, have mercy on us. 
\end{verse}