\section{after the our father}

\begin{liturgicaltext}
    \priest For Thine is the kingdom, and the power, and the glory: of the Father, and of the Son, and of the Holy Spirit, now and ever, and unto the ages of ages. 
    \choir \lilypondfile[insert=inline, inline-staffsize=20, valign=top]{lilypond/files/99 litanies/obikhod/litany-obikhod-amen.ly}
    \priest Peace be unto all.
    \choir \lilypondfile[insert=inline, inline-staffsize=20, valign=top]{lilypond/files/99 litanies/obikhod/litany-obikhod-andto.ly}
    \deacon Let us bow our heads unto the Lord.
    \choir \lilypondfile[insert=inline, inline-staffsize=20, valign=top]{lilypond/files/99 litanies/obikhod/litany-obikhod-tothee.ly} \reversemarginpar\marginnote{\rubric{\small Slowly, always}}[1.5cm] \pagebreak
\end{liturgicaltext}
\begin{semisecret}
    \begin{secretprayerbasil}
        We give thanks unto Thee, O King invisible, who by Thine immeasurable might hast created all things, and in the multitude of Thy mercies hast brought all things from non-being into being; do Thou Thyself, O Master, look from heaven upon them that have bowed their heads unto Thee, for thy have not bowed down unto flesh and blood, but unto Thee, the awesome God. Do Thou therefore, O Master, distribute these Things here set forth unto us all for good, according to the need of each; sail with them that voyage, travel with them that journey, heal the sick, O Thou Physician of our souls and bodies.
        \switchcolumn
        O Master, Lord, the Father of compassions and the God of all comfort: bless, sanctify, guard, strengthen, and fortify those who have bowed their heads unto thee. Withdraw them from every evil deed; apply them to every good work and make them worthy to partake without condemnation of these, Thy most pure and life creating Mysteries, unto the remission of their sins, and unto communion of the Holy Spirit.
    \end{secretprayerbasil}
\end{semisecret}
\begin{liturgicaltext}
    \priest Through the grace and compassions and love for mankind of Thine Only-begotten Son, with Whom Thou art blessed, together with Thy most holy, and good, and life-creating Spirit, now and ever, and unto the ages of ages.
    \choir \lilypondfile[insert=inline, inline-staffsize=20, valign=top]{lilypond/files/28-afterourfather/double-amen.ly} \pagebreak
    \deacon Let us attend!
    \priest Holy Things are for the holy. 
    \choir
\end{liturgicaltext}
\lilypondfile{lilypond/files/28-afterourfather/one-is-holy.ly}