\section{usual beginning}

\begin{liturgicaltext}
    \priest Blessed is our God, always, now and ever, and unto the ages of ages.
    \reader Amen. Glory to Thee, our God, glory to Thee.
    \item[] O Heavenly King, Comforter, Spirit of Truth, Who art everywhere present and fillest all things, Treasury of good things, and Giver of life: come and dwell in us, and cleanse us of all impurity, and save our souls, O Good One.
    \item[] Holy God, Holy Mighty, Holy Immortal, have mercy on us \rubric{(thrice)}
    \item[] Glory to the Father, and to the Son, and to the Holy Spirit, both now and ever, and unto the ages of ages. Amen.
    \item[] O Most-Holy Trinity, have mercy on us; O Lord, blot out our sins; O Master, pardon our iniquities; O Holy One, visit and heal our infirmities for Thy Name's sake.
    \item[] Lord have mercy \rubric{(thrice)}
    \item[] Glory to the Father, and to the Son, and to the Holy Spirit, both now and ever, and unto the ages of ages. Amen.
    \item[] Our Father, Who art in heaven, hallowed be Thy name. Thy kingdom come. Thy will be done, on earth as it is in heaven. Give us this day our daily bread, and forgive us our debts, as we forgive our debtors. And lead us not into temptation, but deliver us from the evil one.
    \priest For Thine is the kingdom, and the power, and the glory: of the Father, and of the Son, and of the Holy Spirit, now and ever, and unto the ages of ages.
    \reader Amen. Lord, have mercy. \rubric{(twelve times)}
    \item[] Glory to the Father, and to the Son, and to the Holy Spirit, both now and ever, and unto the ages of ages. Amen.
    \item[] O come, let us worship God our King.
    \item[] O come, let us worship and fall down before Christ our King and God.
    \item[] O come, let us worship and fall down before Christ Himself, our King and God.
\end{liturgicaltext}
